Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-03 popl24/intro.tex
checkpoint

In \ref{section-minicat} we develop a new probabilistic programming
language $\minifed$ for defining synchronous distributed protocols
over the binary field. The syntax and semantics provides a succinct
account of \emph{views} and (synchronous) messaging between protocol
\emph{clients}. In this Section we consider small example protocols
including oblivious transfer, communications encryption with one-time
pads, and additive secret sharing. In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we then formulate a novel hyperproperty of program execution
traces, called \emph{noninterference modulo output ($\NIMO$)} that we
demonstrate implies passive simulator security. In Section
\ref{section-bruteforce} we define a brute force mechanism for
verifying passive security in $\minifed$ protocols, that is also
amenable to HPC optimizations via translation of $\minifed$ protocols
into Datalog \cnote{I think this Section can be on the chopping block
  for space savings, since it's based on truth table
  computation/Datalog semantics.}.

>>>>

In Section \ref{section-minicat} we develop a new probabilistic programming
language $\minifed$ for defining synchronous distributed protocols
over the binary field. The syntax and semantics provides a succinct
account of \emph{views} and (synchronous) messaging between protocol
\emph{clients}. In this Section we consider small example protocols
including oblivious transfer, communications encryption with one-time
pads, and additive secret sharing. In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we then formulate a novel hyperproperty of program execution
traces, called \emph{noninterference modulo output ($\NIMO$)} that we
demonstrate implies passive simulator security. In Section
\ref{section-bruteforce} we define a brute force mechanism for
verifying passive security in $\minifed$ protocols, that is also
amenable to HPC optimizations via translation of $\minifed$ protocols
into Datalog \cnote{I think this Section can be on the chopping block
  for space savings, since it's based on truth table
  computation/Datalog semantics.}.
